---
title: "Alcohol vs Seat choice"
author: "Ulises Morales"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The fancy box plot reinforces the previous box plot shows the median of the average use of alcohol is greater for students sitting in the back compared to students sitting in the front seat. The fancy box plot's notches show how big the standard deviation is for students sitting in the back drink more than the other students.  

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
To reinforce the....The students sitting in the front on average consume alcohol 1.8 times a week, the middle consume on average 3.3 times a week, and the back consumes on average 8.5 times a week. The standard deviation for the front is 3.8, middle is 6.2, and the last is 12.5, reinforcing the second box plot with the students siting further from the front the greater the consumption of alcohol is.   
## Inferential Tests



## Conclusions


