---
title: "Alcohol vs Seat choice"
author: "Ulises Morales"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The fancy box plot reinforces the previous box plot shows the median of the average use of alcohol is greater for students sitting in the back compared to students sitting in the front seat. The fancy box plot's notches show how big the standard deviation is for students sitting in the back drink more than the other students.  

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
To reinforce the....The students sitting in the front on average consume alcohol 1.8 times a week, the middle consume on average 3.3 times a week, and the back consumes on average 8.5 times a week. The standard deviation for the front is 3.8, middle is 6.2, and the last is 12.5, reinforcing the second box plot with the students siting further from the front the greater the consumption of alcohol is.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
We got a low P value for the anova test which means we are not done yet. The P value means that there are at least two rows where the alcohol consumption is significantly different between them. 

```{r}
plot(TukeyHSD(model1))
```
  
If you look at the front to the back the mean level is different the back is drinking around 12 to 4 drinks more than the front is. The back is drinking around 10 to 3 drinks more than the middle. It doesn't look like there is any difference between the middle and the front because 0 is inside the confidence level of the difference. 

## Conclusions

We were given that the problem was a numerical~categorical problem and we uploaded the helper file. We looked at each plot and figured out which row drank more than the others. We figured out the back row drank more and the conclusion came from the Tukey HSD test. 
